Supplement to: Learning to Infer Graphics Programs from Hand-Drawn Images

### 2018-10-18 supplement.tex
almost, ready!

% to compile a camera-ready version, add the [final] option, e.g.:
%\usepackage{iclr2018_conference,times}
\usepackage{nips_2017}

@@

\section{Why not use an end--to--end solution?}

@@

We synthesized programs for the top 10 specs
output by the deep network.  Learning this prior over programs can
help correct mistakes made by the neural network, and also
occasionally introduces mistakes of its own; see
Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
example of the kinds of corrections that it makes. On the whole
it modestly improves our Top-1 accuracy from 63\% to 67\%.  Recall that
from Fig. 6 of the main paper that the best improvement
in accuracy we could possibly get is 70\% by looking at the top 10 specs. 
\begin{figure}[h]\centering
  \begin{minipage}{6cm}
      \includegraphics[width = 5cm]{figures/programSuccess7.png}
  \includegraphics[width = 5cm]{figures/programSuccess16.png}
    \end{minipage}
  \caption{Left: hand drawing. Center: interpretation favored by the deep network. Right: interpretation favored after learning a prior over programs. Our learned prior favors shorter, simpler programs, thus (top example) continuing the pattern of not having an arrow is preferred, or (bottom example) continuing the binary search tree is preferred.}\label{exampleOfProgramCorrectingMistake}
\end{figure}
\pagebreak

@@

We parameterize the space of policies as a simple log bilinear model:
\begin{equation}
  \pi_{\theta}(\sigma |S)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{spec}}(S)\right)
\end{equation}
where:
\begin{align*}
  \phi_{\text{params}}(\sigma ) = [&\indicator [\sigma \text{ can loop}] ;\\
    &\indicator [\sigma \text{ can reflect}];\\
    &\indicator [\sigma \text{ is incremental}] ; \\
    &\indicator [\sigma \text{ has depth bound }1];\indicator [\sigma \text{ has depth bound }2];\indicator [\sigma \text{ has depth bound }3];]\\
  \phi_{\text{spec}}(S) = [&\text{\# circles in }S;\text{\# rectangles in }S;\text{\# lines in }S;1]
  \end{align*}
where the meaning of ``incremental'' is described in the next section.
\subsection{Incremental Solving}
Rather than give the sketch program synthesizer the entire spec all at once,
we can instead give it subsets of the spec (subsets of the objects in the image)
and ask it to synthesize a program for each subset.
We then concatenate the resulting programs from each subset to get a program that explains the entire image,
and we call this strategy ``incremental solving''.
Incremental solving is not guaranteed to be faster,
nor is it guaranteed to find a minimum cost program.
Thus we allow the search policy to decide
what fraction of our search time should be allocated to this incremental approach to program synthesis.
Concretely, we partitioned a spec into its constituent lines, circles, and rectangles.
\subsection{Baseline comparisons}
In addition to the end-to-end baseline,
we compared with a DeepCoder-style baseline (main paper, Section 3.1).
DeepCoder (DC)~\cite{BalGauBroetal16}
is an approach for learning to speed up program synthesizers.
DC models are neural networks that
predict, starting from a spec,
the probability of a DSL component being in a minimal-cost program satisfying the spec.
Writing $\text{DC}(S)$ for the distribution predicted by the neural network,
DC is trained to maximize  the following objective:
\begin{equation}
  \expect_{S\sim\mathcal{D}}\left[\min_{p\in \text{\textsc{Best}}(S)} \sum_{x\in \text{DSL}} \log \left(\indicator\left[x\in p \right] \text{DC}(S)_x + \indicator\left[x\notin p \right] (1 - \text{DC}(S)_x)\right)
    \right]
\end{equation}
where $x$ ranges over DSL components and $\text{DC}(S)_x\in \left[0,1 \right]$  is the probability predicted by the DC model for component $x$ for spec $S$.

Figure~\ref{policyEvaluation} shows histograms of the synthesis time for our model and baselines.

\begin{figure}
  \includegraphics[width = \textwidth]{figures/policyComparison_basic_DC+bias_20.png}
    \caption{Time to synthesize a minimum cost program. Sketch: out-of-the-box performance of Sketch~\citep{solar2008program}. DC: Deep--Coder style baseline that predicts program components, trained like~\cite{BalGauBroetal16}. Oracle:  upper bounds  the performance of any bias--optimal search policy. $\infty = $ timeout. Red dashed line is median time.}
  \end{figure}
\pagebreak
\section{Neural network architecture}

\subsection{High-level overview}
\tikzset{>=latex}
\begin{figure}[t]
  \begin{tikzpicture}
  \node[draw,blue,ultra thick,anchor = west,inner sep=0pt,label=below:Sarget image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(S)$] (canvas) at (0,-4) {};
  \draw[lightgray,ultra thin,step = 0.125] ([xshift = 0.5,yshift = 0.5]canvas.south west) grid ([xshift = -0.5,yshift = -0.5]canvas.north east);
  % draw partial image on canvas
  \draw (0.375cm,-3.25cm) circle (0.125cm);
  \draw (0.625cm,-3.625) circle (0.125cm);
  \draw (0.75cm,-3.375) circle (0.125cm);

%  \node at (canvas.x,canvas.y) {Canvas};
\end{tikzpicture}
\caption{Our neural architecture for inferring the spec of a graphics program from its output. \textcolor{blue}{Blue}: network inputs. Black: network operations. \textcolor{red}{Red}: samples from a multinomial. \texttt{Typewriter font}: network outputs. Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}. STN (spatial transformer network) is a differentiable attention mechanism~\citep{jaderberg2015spatial}.}  \label{architecture}
\end{figure}
For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
\begin{equation}
  \probability_\theta [t_1t_2\cdots t_K | I,S] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(S)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
\end{equation}
where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
the target image, $S$ is a spec, $\theta$ are the
parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
specs factorizes as:
\begin{equation}
  \probability_\theta [S|I] = \prod_{n = 1}^{|S|} \probability_\theta [S_n | I,S_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,S]\label{objective}
\end{equation}
where $|S|$ is the length of spec $S$, the subscripts
on $S$ index drawing commands within the spec (so $S_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
token is emitted by the network to signal that the spec
explains the image.

\subsection{Convolutional network}\label{CNNarchitecture}
The convolutional network takes as input 2 $256\times 256$ images
represented as a $2\times 256\times 256$ volume. These are
passed through two layers of convolutions separated by ReLU
nonlinearities and max pooling:
\begin{itemize}
\item Layer 1: 20 $8\times 8$ convolutions, 2 $16\times 4$ convolutions, 2 $4\times 16$ convolutions. Followed by $8\times 8$ pooling with a stride size of 4.
\item Layer 2: 10 $8\times 8$ convolutions. Followed by $4\times 4$ pooling with a stride size of 4.
\end{itemize}

Training takes a little bit less than a day on a Nvidia TitanX GPU.
The network was trained on $10^5$ synthetic examples.

\begin{comment}
\subsection{Predicting continuous coordinates using Mixture Density Networks}

Our main paper describes a neural model for parsing hand drawings
into~\LaTeX, but comes with the restriction that all of the
coordinates of all the drawing commands are snapped to a $16\times 16$
grid. Now we describe a variant of our model that
can predict continuous real valued coordinates.

The key obstacle to overcome is \emph{multimodality}: if the network
is unsure whether it should predict a coordinate value of $a$ or $b$,
we wish to predict a distribution that splits its mass between $a$ and
$b$, rather than predicting the single value $\frac{a + b}{2}$.  In
the model where everything is snapped to a discrete grid, supporting
this multimodality falls out naturally from our parameterization of
the network predictions (i.e., the network predicts the parameters of
a multinomial distribution). To predict continuous real valued
coordinates we turn to Mixture Density Networks (MDN:~\cite{MDN}).  In
an MDN, a distribution over a real-valued random variable is
parameterized using a mixture of Gaussians, and the deep network
predicts the parameters of the Gaussian mixture.

Concretely,
we modify our autoregressive drawing command decoder to
predict distributions over real-valued coordinates
as:
\begin{equation}
  p(t_n|t_{1:(n - 1)}) = \text{MDN}_{t_1,n} (a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} t_j)\text{, if }n^{\text{th}}\text{ token is continuous}\label{continuousDensityEquation}
\end{equation}
Compare this equation with Equation~\ref{discreteTokenPrediction} to see that we have only
replaced a draw from a multinomial (whose parameters are predicted by an MLP)
with a draw from a mixture of Gaussians (whose parameters are predicted by an MDN).
Otherwise the two models are identical.

For an MDN $i$ with $K$ mixture components that takes as input $x$, we parameterize it's output distribution as:
\begin{eqnarray}
  \text{MDN}_i(x) &=& \sum_{1\leq k\leq K} \pi_{i,k}(x)\times \mathcal{N}(\mu_{i,k}(x),\sigma^2_{i,k}(x))\\
  \mu_{i,k}(x)& = &\text{sigmoid} (W^{\mu_{i,k}}x + b^{\mu_{i,k}}x)\label{mixtureMean}
  \\\sigma^2_{i,k}(x)& = &\log \left(1 + \exp\left(W^{\sigma^2_{i,k}}x + b^{\sigma^2_{i,k}}x\right) \right)
  \\\pi_{i,k}(x)& = &\frac{\exp\left(W^{\pi_{i,k}}x + b^{\pi_{i,k}}x \right)}{\sum_{k'} \exp\left(W^{\pi_{i,k'}}x + b^{\pi_{i,k'}}x \right)}
  \end{eqnarray}
where $W$ with a superscript is a learned weight matrix and $b$ is a
learned bias vector. Notice that Equation~\ref{mixtureMean} normalizes
the predicted means to be within $[0,1]$: this is because we wish to
constrain the predicted coordinates to lie within the plane
$[0,1]^2$. We used $K = 16$ mixture components.

Figure~\ref{syntheticContinuous}  shows the behavior of the MDN variant of our model on noisy synthetic drawings.
Contrast these mediocre results with Figure~4 of the main paper to see that although
our main model is essentially at ceiling for parsing scenes like these,
the MDN variant fares poorly in comparison.
\begin{figure}
  \includegraphics[width = \textwidth]{figures/syntheticContinuous.png}
  \caption{Left column: \LaTeX~output corrupted by noise process designed to resemble the variability is introduced by hand drawings. Right columns: samples from the MDN variant of the model.}\label{syntheticContinuous}
\end{figure}

We evaluated the MDN version of our model on hand drawings by (1)
performing a beam search in order to find the spec maximizing
$\probability [T|I]$, and (2) constraining the predicted coordinates
to lie on the $16\times 16$ grid. We constrain the predicted coordinates
to lie on the grid by integrating the predicted densities about each grid location.
So, using the probability density $p(t_n|t_{1:(n - 1)})$ in Eq.~\ref{continuousDensityEquation},
we compute a probability mass function $\probability [t_n|t_{1:(n - 1)}]$ as:
\begin{equation}
  \probability [t_n = t|t_{1:(n - 1)}] = \int_{t - \frac{1}{2}}^{t + \frac{1}{2}} \mathrm{d}t_n \; p(t_n|t_{1:(n - 1)})\label{constrainingEquation}
\end{equation}
Even after using Eq.~\ref{constrainingEquation} to constrain the predicted coordinates to lie on the $16\times 16$ grid, the MDN variant of the model only produces finished specs for 48/100 of the drawings.
See Figure~\ref{continuousParses} to see the specs recovered by the beam search.

\begin{figure}
  \includegraphics[width = \textwidth]{figures/continuousParses.png}
  \caption{Parsing hand drawings using the MDN variant of our
    model. Black-on-white: hand drawings. White-on-black, below each
    hand drawing: the parse inferred by the model.}\label{continuousParses} 
  \end{figure}
\end{comment}
\subsection{LSTM Baseline}

We train this network by sampling random synthetic scenes for $T_1$,
and then perturbing them in small ways to produce $T_2$.
We minimize the squared loss between the network's prediction and the ground truth symmetric differences.
$T_1$ is rendered in a ``simulated hand drawing'' style which we describe next.

\section{Simulating hand drawings}

\section{Likelihood surrogate for synthetic data}
For synthetic data (e.g., \LaTeX~output)
it is relatively straightforward to engineer an adequate distance measure between images,
because it is possible for the system to discover
drawing commands that exactly match the pixels in the target image.
We use:
\begin{equation}
  -\log L(I_1|I_2) = \sum_{1\leq x\leq 256} \sum_{1\leq y\leq 256} |I_1[x,y] - I_2[x,y]|\begin{cases}
    \alpha\text{, if }$I_1[x,y] > I_2[x,y]$\\
    \beta\text{, if }$I_1[x,y] <  I_2[x,y]$\\
        0\text{, if }$I_1[x,y] = I_2[x,y]$\\
    \end{cases}
  \end{equation}
where $\alpha$, $\beta$ are constants that control the trade-off
between preferring to explain the pixels in the image (at the expense
of having extraneous pixels) and not predicting pixels where they
don't exist (at the expense of leaving some pixels unexplained). Because our sampling procedure incrementally constructs the scene part-by-part,
we want $\alpha > \beta$.
That is, it is preferable to leave some pixels unexplained;
for once a particle in SMC adds a drawing primitive to its spec that is not actually in the latent scene,
it can never recover from this error.
In our experiments on synthetic data we used $\alpha = 0.8$ and $\beta = 0.04$. 
\section{Generating synthetic training data}

For readers wishing to generate their own synthetic training sets,
we refer them to our source code at:~\url{redactedForAnonymity.com}.%https://github.com/ellisk42/TikZ}.

>>>>

% to compile a camera-ready version, add the [final] option, e.g.:
%\usepackage{iclr2018_conference,times}
\usepackage[final]{nips_2017}

@@

\section{Neural network architecture and training}

\subsection{High-level overview}

For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
\begin{equation}
  \probability_\theta [t_1t_2\cdots t_K | I,S] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(S)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
\end{equation}
where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
the target image, $S$ is a spec, $\theta$ are the
parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
specs factorizes as:
\begin{equation}
  \probability_\theta [S|I] = \prod_{n = 1}^{|S|} \probability_\theta [S_n | I,S_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,S]\label{objective}
\end{equation}
where $|S|$ is the length of spec $S$, the subscripts
on $S$ index drawing commands within the spec (so $S_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
token is emitted by the network to signal that the spec
explains the image.
\tikzset{>=latex}
\begin{figure}
  \begin{tikzpicture}
  \node[draw,blue,ultra thick,anchor = west,inner sep=0pt,label=below:Sarget image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(S)$] (canvas) at (0,-4) {};
  \draw[lightgray,ultra thin,step = 0.125] ([xshift = 0.5,yshift = 0.5]canvas.south west) grid ([xshift = -0.5,yshift = -0.5]canvas.north east);
  % draw partial image on canvas
  \draw (0.375cm,-3.25cm) circle (0.125cm);
  \draw (0.625cm,-3.625) circle (0.125cm);
  \draw (0.75cm,-3.375) circle (0.125cm);

%  \node at (canvas.x,canvas.y) {Canvas};
\end{tikzpicture}
\caption{Our neural architecture for inferring the spec of a graphics program from its output. \textcolor{blue}{Blue}: network inputs. Black: network operations. \textcolor{red}{Red}: samples from a multinomial. \texttt{Typewriter font}: network outputs. Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}. STN (spatial transformer network) is a differentiable attention mechanism~\citep{jaderberg2015spatial}.}  \label{architecture}
\end{figure}
\subsection{Convolutional network}\label{CNNarchitecture}
The convolutional network takes as input 2 $256\times 256$ images
represented as a $2\times 256\times 256$ volume. These are
passed through two layers of convolutions separated by ReLU
nonlinearities and max pooling:
\begin{itemize}
\item Layer 1: 20 $8\times 8$ convolutions, 2 $16\times 4$ convolutions, 2 $4\times 16$ convolutions. Followed by $8\times 8$ pooling with a stride size of 4.
\item Layer 2: 10 $8\times 8$ convolutions. Followed by $4\times 4$ pooling with a stride size of 4.
\end{itemize}

Training takes a little bit less than a day on a Nvidia TitanX GPU.
The network was trained on $10^5$ synthetic examples.
\subsection{LSTM Baseline}

\subsection{Generating synthetic training data}

For readers wishing to generate their own synthetic training sets,
we refer them to our source code at:~\url{https://github.com/ellisk42/TikZ}.

%\pagebreak
\section{Generalizing to real hand drawings}
\subsection{Simulating hand drawings}\label{simulatingHandDrawings}

\begin{figure}

\centering\vspace{-0.7cm}  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
    \subcaption{hand drawing}
  \end{minipage}\\
   \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
    \subcaption{rendering of (a)'s inferred spec}
  \end{minipage}\qquad% 
  \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
    \subcaption{noisy rendering of (b)}
  \end{minipage}%
  \caption{Noisy renderings produced in \LaTeX~Ti\emph{k}Z w/ \texttt{pencildraw} package }
    \label{handDrawingExamples} 
\end{figure}

We train this network by sampling random synthetic scenes for $T_1$,
and then perturbing them in small ways to produce $T_2$.
We minimize the squared loss between the network's prediction and the ground truth symmetric differences.
$T_1$ is rendered in a ``simulated hand drawing'' style which Section~\ref{simulatingHandDrawings} describes.
%\pagebreak

We parameterize the space of policies as a simple log bilinear model:
\begin{equation}
  \pi_{\theta}(\sigma |S)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{spec}}(S)\right)
\end{equation}
where:
\begin{align*}
  \phi_{\text{params}}(\sigma ) = [&\indicator [\sigma \text{ can loop}] ;\\
    &\indicator [\sigma \text{ can reflect}];\\
    &\indicator [\sigma \text{ is incremental}] ; \\
    &\indicator [\sigma \text{ has depth bound }1];\indicator [\sigma \text{ has depth bound }2];\indicator [\sigma \text{ has depth bound }3];]\\
  \phi_{\text{spec}}(S) = [&\text{\# circles in }S;\text{\# rectangles in }S;\text{\# lines in }S;1]
  \end{align*}
where the meaning of ``incremental'' is described in the next section.
\subsection{Incremental Solving}
Rather than give the sketch program synthesizer the entire spec all at once,
we can instead give it subsets of the spec (subsets of the objects in the image)
and ask it to synthesize a program for each subset.
We then concatenate the resulting programs from each subset to get a program that explains the entire image,
and we call this strategy ``incremental solving''.
Incremental solving is not guaranteed to be faster,
nor is it guaranteed to find a minimum cost program.
Thus we allow the search policy to decide
what fraction of our search time should be allocated to this incremental approach to program synthesis.
Concretely, we partitioned a spec into its constituent lines, circles, and rectangles.
\subsection{Baseline comparisons}

\subsubsection{DeepCoder-style baseline}

In addition to the end-to-end baseline,
we compared with a DeepCoder-style baseline (main paper, Section 3.1).
DeepCoder (DC)~\cite{BalGauBroetal16}
is an approach for learning to speed up program synthesizers.
DC models are neural networks that
predict, starting from a spec,
the probability of a DSL component being in a minimal-cost program satisfying the spec.
Writing $\text{DC}(S)$ for the distribution predicted by the neural network,
DC is trained to maximize  the following objective:
\begin{equation}
  \expect_{S\sim\mathcal{D}}\left[\min_{p\in \text{\textsc{Best}}(S)} \sum_{x\in \text{DSL}} \log \left(\indicator\left[x\in p \right] \text{DC}(S)_x + \indicator\left[x\notin p \right] (1 - \text{DC}(S)_x)\right)
    \right]
\end{equation}
where $x$ ranges over DSL components and $\text{DC}(S)_x\in \left[0,1 \right]$  is the probability predicted by the DC model for component $x$ for spec $S$.

\subsubsection{End-to-End baseline}

@@

We synthesized programs for the top 10 specs
output by the deep network.  Learning this prior over programs can
help correct mistakes made by the neural network, and also
occasionally introduces mistakes of its own; see
Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
example of the kinds of corrections that it makes. On the whole
it modestly improves our Top-1 accuracy from 63\% to 67\%.  Recall that
from Fig. 6 of the main paper that the best improvement
in accuracy we could possibly get is 70\% by looking at the top 10 specs. 
\begin{figure}[h]\centering
  \begin{minipage}{6cm}
      \includegraphics[width = 5cm]{figures/programSuccess7.png}
  \includegraphics[width = 5cm]{figures/programSuccess16.png}
    \end{minipage}
  \caption{Left: hand drawing. Center: interpretation favored by the deep network. Right: interpretation favored after learning a prior over programs. Our learned prior favors shorter, simpler programs, thus (top example) continuing the pattern of not having an arrow is preferred, or (bottom example) continuing the binary search tree is preferred.}\label{exampleOfProgramCorrectingMistake}
\end{figure}
%\pagebreak

@@

%\pagebreak

%% \begin{comment}
%% \subsection{Predicting continuous coordinates using Mixture Density Networks}

%% Our main paper describes a neural model for parsing hand drawings
%% into~\LaTeX, but comes with the restriction that all of the
%% coordinates of all the drawing commands are snapped to a $16\times 16$
%% grid. Now we describe a variant of our model that
%% can predict continuous real valued coordinates.

%% The key obstacle to overcome is \emph{multimodality}: if the network
%% is unsure whether it should predict a coordinate value of $a$ or $b$,
%% we wish to predict a distribution that splits its mass between $a$ and
%% $b$, rather than predicting the single value $\frac{a + b}{2}$.  In
%% the model where everything is snapped to a discrete grid, supporting
%% this multimodality falls out naturally from our parameterization of
%% the network predictions (i.e., the network predicts the parameters of
%% a multinomial distribution). To predict continuous real valued
%% coordinates we turn to Mixture Density Networks (MDN:~\cite{MDN}).  In
%% an MDN, a distribution over a real-valued random variable is
%% parameterized using a mixture of Gaussians, and the deep network
%% predicts the parameters of the Gaussian mixture.

%% Concretely,
%% we modify our autoregressive drawing command decoder to
%% predict distributions over real-valued coordinates
%% as:
%% \begin{equation}
%%   p(t_n|t_{1:(n - 1)}) = \text{MDN}_{t_1,n} (a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} t_j)\text{, if }n^{\text{th}}\text{ token is continuous}\label{continuousDensityEquation}
%% \end{equation}
%% Compare this equation with Equation~\ref{discreteTokenPrediction} to see that we have only
%% replaced a draw from a multinomial (whose parameters are predicted by an MLP)
%% with a draw from a mixture of Gaussians (whose parameters are predicted by an MDN).
%% Otherwise the two models are identical.

%% For an MDN $i$ with $K$ mixture components that takes as input $x$, we parameterize it's output distribution as:
%% \begin{eqnarray}
%%   \text{MDN}_i(x) &=& \sum_{1\leq k\leq K} \pi_{i,k}(x)\times \mathcal{N}(\mu_{i,k}(x),\sigma^2_{i,k}(x))\\
%%   \mu_{i,k}(x)& = &\text{sigmoid} (W^{\mu_{i,k}}x + b^{\mu_{i,k}}x)\label{mixtureMean}
%%   \\\sigma^2_{i,k}(x)& = &\log \left(1 + \exp\left(W^{\sigma^2_{i,k}}x + b^{\sigma^2_{i,k}}x\right) \right)
%%   \\\pi_{i,k}(x)& = &\frac{\exp\left(W^{\pi_{i,k}}x + b^{\pi_{i,k}}x \right)}{\sum_{k'} \exp\left(W^{\pi_{i,k'}}x + b^{\pi_{i,k'}}x \right)}
%%   \end{eqnarray}
%% where $W$ with a superscript is a learned weight matrix and $b$ is a
%% learned bias vector. Notice that Equation~\ref{mixtureMean} normalizes
%% the predicted means to be within $[0,1]$: this is because we wish to
%% constrain the predicted coordinates to lie within the plane
%% $[0,1]^2$. We used $K = 16$ mixture components.

%% Figure~\ref{syntheticContinuous}  shows the behavior of the MDN variant of our model on noisy synthetic drawings.
%% Contrast these mediocre results with Figure~4 of the main paper to see that although
%% our main model is essentially at ceiling for parsing scenes like these,
%% the MDN variant fares poorly in comparison.
%% \begin{figure}
%%   \includegraphics[width = \textwidth]{figures/syntheticContinuous.png}
%%   \caption{Left column: \LaTeX~output corrupted by noise process designed to resemble the variability is introduced by hand drawings. Right columns: samples from the MDN variant of the model.}\label{syntheticContinuous}
%% \end{figure}

%% We evaluated the MDN version of our model on hand drawings by (1)
%% performing a beam search in order to find the spec maximizing
%% $\probability [T|I]$, and (2) constraining the predicted coordinates
%% to lie on the $16\times 16$ grid. We constrain the predicted coordinates
%% to lie on the grid by integrating the predicted densities about each grid location.
%% So, using the probability density $p(t_n|t_{1:(n - 1)})$ in Eq.~\ref{continuousDensityEquation},
%% we compute a probability mass function $\probability [t_n|t_{1:(n - 1)}]$ as:
%% \begin{equation}
%%   \probability [t_n = t|t_{1:(n - 1)}] = \int_{t - \frac{1}{2}}^{t + \frac{1}{2}} \mathrm{d}t_n \; p(t_n|t_{1:(n - 1)})\label{constrainingEquation}
%% \end{equation}
%% Even after using Eq.~\ref{constrainingEquation} to constrain the predicted coordinates to lie on the $16\times 16$ grid, the MDN variant of the model only produces finished specs for 48/100 of the drawings.
%% See Figure~\ref{continuousParses} to see the specs recovered by the beam search.

%% \begin{figure}
%%   \includegraphics[width = \textwidth]{figures/continuousParses.png}
%%   \caption{Parsing hand drawings using the MDN variant of our
%%     model. Black-on-white: hand drawings. White-on-black, below each
%%     hand drawing: the parse inferred by the model.}\label{continuousParses} 
%%   \end{figure}
%% \end{comment}
